---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

First we must unzip the file with the data and read from it. Knowing that some
data is missing, we shall also tidy the data so there are no missing values 
when we start analyzing the data.

```{r echo=TRUE}
unzip("activity.zip")
data <- read.csv("activity.csv")
clean_data <- data[complete.cases(data) == TRUE,]
```


## What is mean total number of steps taken per day?

Here, we will first create a histogram of the total steps taken in a day, 
after which we will calculate the mean. Since the data is given in 5-minute
intervals, first we must aggregate the steps in all those intervals in a day
and then create the histogram.

```{r echo=TRUE}
total_steps <- aggregate(steps ~ date, data = clean_data, FUN = sum)
hist(total_steps$steps, main = "Total Steps Taken In A Day", xlab = "Steps")
mean_steps <- mean(total_steps$steps)
```

The mean number of steps taken in a day is `{r mean_steps}`.


## What is the average daily activity pattern?

Now we need to create a time series graph of the 5-minute intervals on the
x-axis and the average steps taken in that interval across all days on the
y-axis. Again, we will aggregate the data, but this time it'll be according
to the interval rather than the day.

```{r echo=TRUE}
average_steps <- aggregate(steps ~ interval, data = clean_data, FUN = mean)
plot(average_steps$interval, 
     average_steps$steps, 
     type = "l", 
     main = "Average Steps Across All Days Per Interval", 
     xlab = "Interval", 
     ylab = "Average Steps")
```


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
